SCM plan for a troubling company

### 2012-01-11 article.tex
11
More CI

\documentclass[a4paper,10pt]{article}
\usepackage[utf8x]{inputenc}

@@

\begin{abstract}

Many companies, especially the small ones, don't see the benefits of SCM in their company and decides to not use it.
This company however have now seen the light and need help to implement it.
This report goes through some aspects in this implementation and focus on a relatively small software company of 40-50 employees.
We analyze some of their problems and come up with solutions in the form of a configuration plan.

\end{abstract}
\newpage

@@

Kanske lite diagram visande CI

Binären måste kontrolleras, dokumentation i versionskontroll också
Design dokument, diagram måste numreras/hanteras

Since we will be implementing the SCM plan iteratively we will start off with some baselines.

-documentation

-source code
Levereras som binär + dokumentation.
Mjukvara har inbyggd ``labelling''

\subsection{Version control}
Med lämplig mjukvara för kod + dokumentation.
Design dokument binära och hanterasw av icke-kodare (akm) bättre med central filserver+versionsnummer manuellt.

@@

Since this company is relatively small, the extent of CCB and it's usage will be somewhat limited in contrary to the general idea of a CCB.
The CCB consist of the normal lineup with: chairperson, secretary, members and specialists \cite{daniels}. We will select the project manager
to be the chairman and the secretary will be the configuration manager in the company. The project manager will appoint appropriate people to be
members of the CCB and specialists will be contacted on a ``when needed''-basis. There will likely be one representative from each module with the exception
that some modules representatives will be considered experts instead, so that they will not be needed for each meeting.

The software in our case is as described earlier divided into modules. Each module consists of around five developers and they're all
located in the same working area. The changes made on this level are traced through commit-comments and the discussion is taken within
the group orally.

The CCB are only involved when it comes to changes that cover more than one module (the API between modules is modified).
In the case that the CCB gets involved, it will pretty much handle change requests that traditional way, namely:

\begin{enumerate}
 \item A change is submitted to the SCM-manager.
 \item The SCM-manager decides if this change needs a meeting.
 \item If a meeting is needed, one is planned.
 \item On the meeting the chairman takes input and decide to approve or note depending on the input.
\end{enumerate}

% Hur stor ccb?
% Hur rigorös CR kontroll?

>>>>

\documentclass[a4paper,11pt]{article}
\usepackage[utf8x]{inputenc}

@@

\begin{abstract}
Many companies, especially the small ones, don't see the benefits of SCM in their company and decides to not use it.
This company however have now seen the light and need help to implement it.
This report goes through some aspects in this implementation and focus on a relatively small software company of 40-50 employees.
We analyze some of their problems and come up with solutions in the form of a configuration plan.
\end{abstract}
\newpage

@@

The configuration identification for the software part is quite straightforward where every module is it's own configuration item and can be subdivided in the files as the next step of the hierarchy.
For the files the filenames and their directories provides a natural naming and an SCM-tool makes this easy to keep track of. The various modules are then combined and this can be kept in the tool as well or be managed manually.
As the documentation actually is tied to the code and it's versions it should, if possible be controlled in the same system to keep it in sync with the code.
The next higher level of configutration control needed is the release level where the build environment and the actual produced binaries together with the released documentation.
This also needs to be documented and controlled in some way as the released models are supported for some years at least.

\subsection{Other items}

As the delivered product is in form of binaries and documentation for inclusion in a larger product there is not much other releasables to control.
However to structure the change process and design of new features design and specification documents are created for communication between customer and the company as well as between internal designers and the coders. These needs to be versioned and saved as well to be able to verify that the product performs according to the specifications.

@@

Since this company is relatively small, the extent of CCB and it's usage will be a somewhat limited in contrary to the general idea of a CCB.
The CCB consist of the normal lineup with: chairperson, secretary, members and specialists \cite{daniels}. We will select the project manager
to be the chairman and the secretary will be the configuration manager in the company. The project manager will appoint appropriate people to be
members of the CCB and specilists will be contacted on a ``when needed''-basis.

Not every change will be handled by the CCB in our case

Hur stor ccb?
Hur rigorös CR kontroll?
